---
output:
  html_document:
    keep_md: yes
    toc: no
    self_contained: yes
  pdf_document:
    toc: yes
---

## imputeTestbench

#### *Neeraj Bokde, neerajdhanraj@gmail.com, Marcus W. Beck, beck.marcus@epa.gov*

[![Travis-CI Build Status](https://travis-ci.org/fawda123/imputeTestbench.svg?branch=master)](https://travis-ci.org/fawda123/imputeTestbench)

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/fawda123/imputeTestbench?branch=master&svg=true)](https://ci.appveyor.com/project/fawda123/imputeTestbench)

[![Downloads from the RStudio CRAN mirror](http://cranlogs.r-pkg.org/badges/grand-total/imputeTestbench)](https://CRAN.R-project.org/package=imputeTestbench)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the development repository for the imputeTestbench package.  This package provides a testbench for comparing imputation methods for missing data in univariate time series. 

The development version of this package can be installed from GitHub:

```{r, eval = FALSE}
install.packages('devtools')
library(devtools)
install_github('neerajdhanraj/imputeTestbench', ref = 'development')
```

The current release can be installed from CRAN:

```{r, eval = FALSE}
install.packages('imputeTestbench')
```

#### Basic use

The core function is `impute_errors()`.  See the help documentation for more details.

```{r message = F}
library(imputeTestbench)
a <- impute_errors(data = nottem)
a
plot_errors(a, plotType = 'line')
```

#### Citation

Neeraj Bokde and Marcus W. Beck (2016). imputeTestbench: Test Bench for the comparison of imputation methods. R package version 3.0. http://www.neerajbokde.com/cran/imputetestbench

#### Bug reports 

Please submit any bug reports (or suggestions) using the [issues](https://github.com/neerajdhanraj/imputeTestbench/issues) tab of the GitHub page.

#### License

This package is released in the public domain under the creative commons license CC0.
